Efficiently Handling Guards in the Low Level Design of RPython's Tracing JIT

### 2012-08-10 talk/vmil2012/paper.tex
update caption
tweak figures and tables

\subsection{Frequency of Guards}
\label{sub:guard_frequency}
\begin{figure*}
    \include{figures/benchmarks_table}
    \caption{Benchmark Results}
    \label{fig:benchmarks}
\end{figure*}

@@

\subsection{Overhead of Guards}
\label{sub:guard_overhead}
\begin{figure}
    \include{figures/resume_data_table}
    \caption{Resume Data sizes in KiB}
    \label{fig:resume_data_sizes}
\end{figure}

@@

\begin{figure}
    \include{figures/backend_table}
    \caption{Total size of generated machine code and guard data}
    \label{fig:backend_data}
\end{figure}

@@

\begin{figure}
    \include{figures/failing_guards_table}
    \caption{Failing guards}
    \label{fig:failing_guards}
\end{figure}

>>>>

\subsection{Frequency of Guards}
\label{sub:guard_frequency}
\begin{figure*}
    \include{figures/benchmarks_table}
    \caption{Number of operations in the recorded traces and the relative amount of guards before and after optimizations}
    \label{fig:benchmarks}
\end{figure*}

@@

\subsection{Overhead of Guards}
\label{sub:guard_overhead}
\begin{figure}
    \include{figures/resume_data_table}
    \caption{Resume data sizes}
    \label{fig:resume_data_sizes}
\end{figure}

@@

\begin{figure}
    \include{figures/backend_table}
    \caption{Total size of generated machine code and resume data}
    \label{fig:backend_data}
\end{figure}

@@

\begin{figure}
    \include{figures/failing_guards_table}
    \caption{Failing guards relative to the total number of guards}
    \label{fig:failing_guards}
\end{figure}
